HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-18 paper/main.tex
updated style, natbib citations

\documentclass[11pt]{article}
\usepackage{acl2016}
\usepackage{amsmath}
\usepackage{paralist}
\usepackage{subfig}
\usepackage{times}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{url}
\usepackage{pgfplotstable}
%\usepackage{hyperref}
\usepackage{color}
\usepackage{lipsum,adjustbox}
\listfiles

@@

\def\perscite#1{\newcite{#1}}
\def\parcite#1{\cite{#1}}
\def\inparcite#1{\newcite{#1}}

@@

Human judgement is the most important criterion for
estimating the quality of an MT system.
Nevertheless, common measures for human MT evaluation, such as adequacy and fluency judgements
or the relative ranking of possible translations, are problematic in two ways.
First, as the quality of translation is determined by multiple factors, it is difficult
to assign a single number that quantifies the quality of the entire sentence. This
is indeed reflected in the diminishing inter-annotator agreement (IAA) rates of human ranking measures
%as a function of
with
the sentence length \cite{Bojar:2011}.
Second, a sentence-level quality score does not indicate what parts of the sentence
are badly translated, and so cannot inform developers in repairing these errors.

These problems are partially addressed by measures that decompose over parts of the evaluated
translation. For automatic measures,
these are often words or n-grams, for manual measures some structural
information is taken into account \parcite{machacek:bojar:segranks:2015}.
% the following is specific to automatic measures:
%quantifying the overlap of its sub-parts relative a reference translation.
A promising line of research decomposes
%More recent work on MT evaluation proposed measures
%that decompose
over semantically defined units,
quantifying the similarity of the output and the reference in terms of
their verb argument structure; the most notable of these measures is
HMEANT \cite{lo2011structured}.
% SAVING SPACE:
% \XXX{Do we want to cut the following shorter?}
% However, 
% their focus on verb argument structures misses many semantic phenomena
% (such as inter-clause linkage and nominal argument structures), providing
% only
% a limited perspective on the semantic similarity between the translation and reference.
% Also, assigning semantic structure to an MT output, especially a poor one,
% is difficult and arguably ill-defined.

We propose the Human UCCA-based MT Evaluation (HUME) metric,
a human evaluation measure that decomposes over the semantic units of the sentence.
Semantic units are defined according to the 
UCCA scheme \cite{abend2013universal}, an appealing candidate for semantic analysis,
due to its cross-linguistic applicability, support for rapid annotation, and coverage
of many fundamental semantic phenomena, such as verbal, nominal and adjectival
argument structures and their inter-relations.

@@

%These difficulties have motivated the definition of a human measure that decomposes over
%the semantic structure of the sentence, rather than its n-grams. The most notable attempt of
%this type is the MEANT measure, and its human variant HMEANT
%\cite{lo2010evaluating,lo2011structured,Lo2011meant,lo2013meant}, which quantifies the
%similarity between the output translation and a reference translation in terms of the similarity
%between their verbal argument structures
%While the measure addresses the two major shortcomings
%detailed above, it is unable to capture semantic differences which do not show up in
%the verb-argument structure, including several very frequent phenomena, such as
%inter-clause linkage, nominalizations and copula clauses
%(see \secref{sec:hmeant_comp}).
%Another shortcoming of MEANT is its reliance on semantically annotating MT output,
%which is often unintelligible. Finally, measures based on a comparison to a
%reference translation
%are necessarily incomplete, as they compare to a small number of references
%out of the the huge number of possible translations a sentence may have
%\cite{dreyer2012hyter}.

\paragraph{Machine Translation Evaluation.}
%MT evaluation has been traditionally pursued through human-based
%evaluation that quantifies the adequacy of the translation in preserving the meaning 
%of the source sentence, and its fluency as a sentence in the target language \cite{lopez2008statistical}.
Human evaluation is generally done by ranking the outputs of multiple systems
e.g., in the WMT tasks \cite{bojar2015findings}, or by giving
adequacy/fluency scores to each translation, a procedure recently improved
by \newcite{graham2015improving}.
However, while providing the gold standard for MT evaluation, human evaluation
is not a scalable solution.
%and is infeasible where a wide variety of systems or parameter settings are to be evaluated.
% has motivated the construction of cheaper methods that correlate with human
%judgement.

Scalability is addressed by employing automatic and semi-automatic approximations of human
judgements. Commonly, such scores decompose over the sub-parts of
the translation, and quantify how many of these sub-parts appear in a manually created reference translation.
This decomposition allows system developers
to localize the errors, or at least unconfirmed parts within the translation.
The most commonly used measures decompose over n-grams or individual words, e.g., 
BLEU \cite{Papineni:2002}, NIST \cite{Doddington:2002} and METEOR  \cite{Banerjee:2005}.
Another common approach is to determine the similarity between the reference and translation
by applying string edit distance \cite{snover2006study}.
While these measures stimulated much progress in MT research by allowing
the evaluation of massive-scale experiments, the focus on words and n-grams does
not provide a good estimate of semantic correctness, and may favour shallow string-based
MT models.

@@

In order to address this shortcoming, more recent work quantified
the similarity of the reference and translation in terms
of their structure. \newcite{liu2005syntactic} took a syntactic approach, 
using dependency grammar, and
\newcite{owczarzak2007evaluating} took a similar approach using lexical-functional grammar structures.
\newcite{gimenez2007linguistic} proposed to combine multiple types of information,
capturing the overlap between the translation and reference in terms of their
semantic (predicate-argument structures), lexical and morphosyntactic features.

@@

% UCCA Motivation
UCCA is a natural candidate for defining a semantic
MT evaluation measure for a number of reasons. 
First, it defines an intuitive set of categories
that can be reliably annotated by non-experts, after as little as two hours
of training \cite{marinotti2014}.
Second, UCCA is a cross-linguistically applicable scheme, seeking to
represent what is shared between languages
by building on linguistic typological theory, and specifically on ``Basic Linguistic Theory''
\cite{Dixon:10a,Dixon:10b,Dixon:12}.
The cross-linguistic applicability of UCCA has been tested in annotations of
English, French, German and Czech.
Third, the scheme has been shown to be semantically stable
in translation: UCCA annotations of translated text usually contain the same set of relationships
\cite{sulem2015conceptual}. This indicates that the scheme reflects
a common layer of representation that in a correct translation
is mostly shared between the translation and the source.

@@

The Abstract Meaning Representation (AMR) scheme \cite{banarescu2013abstract}
shares much of UCCA's motivation for defining a more complete semantic annotation.
However, using AMR is not optimal for defining a decomposition of a sentence into semantic
units as it does not ground its semantic symbols in the text,
thus does not provide clear decomposition of the sentence into sub-units.
Also, AMR is more fine-grained than UCCA and consequently harder to annotate.
Other approaches pursued a grounded representation of semantics,
and have generally represented semantic structures as bi-lexical dependencies.
Examples include the tectogrammatical layer \parcite{sgallhp:1986} used in the Prague dependency
treebanks, e.g. the Czech-English one \parcite{hajic2012announcing}, as well
as dependencies derived from Minimal Recursion Semantics representations \parcite{oepen2006discriminant}.
Nevertheless, despite their appeal as deep and intuitive means for semantic representation,
these approaches require linguistic expertise for their annotation, due to the intricate and
fine-grained distinctions they provide, and so we argue they are less suitable as a basis
for an interpretable MT evaluation.

%\newcite{Basile:12} attempted to make some aspects of the semantic annotation more accessible,
%but to our knowledge no results of this brand have been reported.

@@

For each of the four language pairs under consideration  we built phrase-based MT systems
using Moses \cite{Koehn:2007}. We used large training sets extracted from OPUS \cite{tiedemann:2009}, and
the data sets released for the WMT14 medical translation task \cite{bojar-EtAl:2014:W14-33}, to provide between
45 and 85 million sentences of training data, depending on language pair.
%\oa{I think we should probably
%  say how many in each.}.
% ... if someone asks us to do so...

@@

On the other hand, HUME 
needs the semantic annotation
done once for a given source sentence, whereas for the HMEANT set-up, every new
MT output has to be structurally annotated.\oa{we can give some empirical data here.
  In the WMT 13 experiment, Lexi and Barry report a little over 3 mins of annotation
  per sentence + 3 translations. HUME annotation is about 2-4 minutes per sentence.
  UCCA annotation by trained annotators is about 700 tokens/hour (we didn't
  check it for individual sentences), but that's done only once so it should be amortized.}

@@

One of such alternative formalisms is
Abstract Meaning Representation 
%%% Macro broken?
%(AMR; \inparcite{banarescu2013amr}). 
\cite{banarescu2013amr}. 
AMR is being actively developed with 
%the view to 
a view towards
using it as a way of generating 
translations but AMR graphs are not aligned to the words in the sentences. Having more abstract semantic structures 
makes the link between source words, target words, and structures more complex and potentially less useful. 
Furthermore, AMR  has been developed mainly with English in mind, and it remains
to be seen how universal AMR graphs are. See
\shortcite{amr:interlingua:lrec:2014} for first observations of divergences
between English 
%vs.
vs.\ 
Chinese and
Czech AMRs.

Another possible semantic framework for this kind of MT evaluation is Semantic
Role Labelling 
%(SRL; \inparcite{palmer2010semantic}).
\cite{palmer2010semantic}.
SRL has been used in a human translation metric called HMEANT~\cite{lo2011structured}. 
HMEANT uses semantic role labels
to measure how much of the “who, why, when,
where” has been preserved in translation. Annotators are instructed to identify verbs as
heads of semantic frames. Then they attach role
fillers to the heads and finally they align heads
and role fillers in the candidate translation with
those in a reference translation. Using SRL for evaluating SMT has a number of
disadvantages as explored by
\shortcite{birch-EtAl:2013:WMT} for German, \shortcite{bojar:wu:ssst:2012} for
Czech and by \shortcite{chuchunkov-tarelkin-galinskaya:2014:SSST-8} for Russian.
The most important drawbacks are as follows:
\begin{itemize}
\item SRL frames are based around a verb which is particularly problematic for
copular verbs and  when verbs are translated correctly as nouns or correctly
omitted (the verb ``to be'' in some Russian constructions).
\item SRL frames do not cover the entire source sentence and the semantic structure is
therefore not completely defined, importantly links between frames are not
considered and prepositional phrases which attach to nouns are not marked.
\item Even considering a limited set of eleven roles (agent, patient,
experiencer, locative etc.) is problematic because we cannot assume that these roles will 
 remain stable across different languages. 
 When looking at an automatically parsed  English-Chinese  parallel corpora,
 it was shown that 8.7\% of the arguments do not preserve their semantic roles~\cite{fung2006automatic}. 
\end{itemize}

@@

\bibliography{main}
\bibliographystyle{acl2016}

>>>>

\documentclass[11pt]{article}
\usepackage{acl2016}
\usepackage[round]{natbib}
\usepackage{amsmath}
\usepackage{paralist}
\usepackage{subfig}
\usepackage{times}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{url}
\usepackage{pgfplotstable}
%\usepackage{hyperref}
\usepackage{color}
\usepackage{lipsum,adjustbox}
\listfiles

@@

\def\perscite#1{\citet{#1}}
\def\parcite#1{\citep{#1}}
\def\inparcite#1{\citealp{#1}}

@@

Human judgement is the most important criterion for
estimating the quality of an MT system.
Nevertheless, common measures for human MT evaluation, such as adequacy and fluency judgements
or the relative ranking of possible translations, are problematic in two ways.
First, as the quality of translation is determined by multiple factors, it is difficult
to assign a single number that quantifies the quality of the entire sentence. This
is indeed reflected in the diminishing inter-annotator agreement (IAA) rates of human ranking measures
%as a function of
with
the sentence length \parcite{Bojar:2011}.
Second, a sentence-level quality score does not indicate what parts of the sentence
are badly translated, and so cannot inform developers in repairing these errors.

These problems are partially addressed by measures that decompose over parts of the evaluated
translation. For automatic measures,
these are often words or n-grams, for manual measures some structural
information is taken into account \parcite{machacek:bojar:segranks:2015}.
% the following is specific to automatic measures:
%quantifying the overlap of its sub-parts relative a reference translation.
A promising line of research decomposes
%More recent work on MT evaluation proposed measures
%that decompose
over semantically defined units,
quantifying the similarity of the output and the reference in terms of
their verb argument structure; the most notable of these measures is
HMEANT \parcite{lo2011structured}.
% SAVING SPACE:
% \XXX{Do we want to cut the following shorter?}
% However, 
% their focus on verb argument structures misses many semantic phenomena
% (such as inter-clause linkage and nominal argument structures), providing
% only
% a limited perspective on the semantic similarity between the translation and reference.
% Also, assigning semantic structure to an MT output, especially a poor one,
% is difficult and arguably ill-defined.

We propose the Human UCCA-based MT Evaluation (HUME) metric,
a human evaluation measure that decomposes over the semantic units of the sentence.
Semantic units are defined according to the 
UCCA scheme \parcite{abend2013universal}, an appealing candidate for semantic analysis,
due to its cross-linguistic applicability, support for rapid annotation, and coverage
of many fundamental semantic phenomena, such as verbal, nominal and adjectival
argument structures and their inter-relations.

@@

%These difficulties have motivated the definition of a human measure that decomposes over
%the semantic structure of the sentence, rather than its n-grams. The most notable attempt of
%this type is the MEANT measure, and its human variant HMEANT
%\parcite{lo2010evaluating,lo2011structured,Lo2011meant,lo2013meant}, which quantifies the
%similarity between the output translation and a reference translation in terms of the similarity
%between their verbal argument structures
%While the measure addresses the two major shortcomings
%detailed above, it is unable to capture semantic differences which do not show up in
%the verb-argument structure, including several very frequent phenomena, such as
%inter-clause linkage, nominalizations and copula clauses
%(see \secref{sec:hmeant_comp}).
%Another shortcoming of MEANT is its reliance on semantically annotating MT output,
%which is often unintelligible. Finally, measures based on a comparison to a
%reference translation
%are necessarily incomplete, as they compare to a small number of references
%out of the the huge number of possible translations a sentence may have
%\parcite{dreyer2012hyter}.

\paragraph{Machine Translation Evaluation.}
%MT evaluation has been traditionally pursued through human-based
%evaluation that quantifies the adequacy of the translation in preserving the meaning 
%of the source sentence, and its fluency as a sentence in the target language
%\parcite{lopez2008statistical}.
Human evaluation is generally done by ranking the outputs of multiple systems
e.g., in the WMT tasks \parcite{bojar2015findings}, or by giving
adequacy/fluency scores to each translation, a procedure recently improved
by \perscite{graham2015improving}.
However, while providing the gold standard for MT evaluation, human evaluation
is not a scalable solution.
%and is infeasible where a wide variety of systems or parameter settings are to be evaluated.
% has motivated the construction of cheaper methods that correlate with human
%judgement.

Scalability is addressed by employing automatic and semi-automatic approximations of human
judgements. Commonly, such scores decompose over the sub-parts of
the translation, and quantify how many of these sub-parts appear in a manually created reference translation.
This decomposition allows system developers
to localize the errors, or at least unconfirmed parts within the translation.
The most commonly used measures decompose over n-grams or individual words, e.g., 
BLEU \parcite{Papineni:2002}, NIST \parcite{Doddington:2002} and METEOR
\parcite{Banerjee:2005}.
Another common approach is to determine the similarity between the reference and translation
by applying string edit distance \parcite{snover2006study}.
While these measures stimulated much progress in MT research by allowing
the evaluation of massive-scale experiments, the focus on words and n-grams does
not provide a good estimate of semantic correctness, and may favour shallow string-based
MT models.

@@

In order to address this shortcoming, more recent work quantified
the similarity of the reference and translation in terms
of their structure. \perscite{liu2005syntactic} took a syntactic approach, 
using dependency grammar, and
\perscite{owczarzak2007evaluating} took a similar approach using lexical-functional grammar structures.
\perscite{gimenez2007linguistic} proposed to combine multiple types of information,
capturing the overlap between the translation and reference in terms of their
semantic (predicate-argument structures), lexical and morphosyntactic features.

@@

% UCCA Motivation
UCCA is a natural candidate for defining a semantic
MT evaluation measure for a number of reasons. 
First, it defines an intuitive set of categories
that can be reliably annotated by non-experts, after as little as two hours
of training \parcite{marinotti2014}.
Second, UCCA is a cross-linguistically applicable scheme, seeking to
represent what is shared between languages
by building on linguistic typological theory, and specifically on ``Basic Linguistic Theory''
\parcite{Dixon:10a,Dixon:10b,Dixon:12}.
The cross-linguistic applicability of UCCA has been tested in annotations of
English, French, German and Czech.
Third, the scheme has been shown to be semantically stable
in translation: UCCA annotations of translated text usually contain the same set of relationships
\parcite{sulem2015conceptual}. This indicates that the scheme reflects
a common layer of representation that in a correct translation
is mostly shared between the translation and the source.

@@

The Abstract Meaning Representation (AMR) scheme \parcite{banarescu2013abstract}
shares much of UCCA's motivation for defining a more complete semantic annotation.
However, using AMR is not optimal for defining a decomposition of a sentence into semantic
units as it does not ground its semantic symbols in the text,
thus does not provide clear decomposition of the sentence into sub-units.
Also, AMR is more fine-grained than UCCA and consequently harder to annotate.
Other approaches pursued a grounded representation of semantics,
and have generally represented semantic structures as bi-lexical dependencies.
Examples include the tectogrammatical layer \parcite{sgallhp:1986} used in the Prague dependency
treebanks, e.g. the Czech-English one \parcite{hajic2012announcing}, as well
as dependencies derived from Minimal Recursion Semantics representations \parcite{oepen2006discriminant}.
Nevertheless, despite their appeal as deep and intuitive means for semantic representation,
these approaches require linguistic expertise for their annotation, due to the intricate and
fine-grained distinctions they provide, and so we argue they are less suitable as a basis
for an interpretable MT evaluation.

%\perscite{Basile:12} attempted to make some aspects of the semantic annotation more accessible,
%but to our knowledge no results of this brand have been reported.

@@

For each of the four language pairs under consideration  we built phrase-based MT systems
using Moses \parcite{Koehn:2007}. We used large training sets extracted from
OPUS \parcite{tiedemann:2009}, and
the data sets released for the WMT14 medical translation task \parcite{bojar-EtAl:2014:W14-33}, to provide between
45 and 85 million sentences of training data, depending on language pair.
%\oa{I think we should probably
%  say how many in each.}.
% ... if someone asks us to do so...

@@

On the other hand, HUME 
needs the semantic annotation
done once for a given source sentence, whereas for the HMEANT set-up, every new
MT output has to be structurally annotated.

%\oa{we can give some empirical data here.
%  In the WMT 13 experiment, Lexi and Barry report a little over 3 mins of annotation
%  per sentence + 3 translations. HUME annotation is about 2-4 minutes per sentence.
%  UCCA annotation by trained annotators is about 700 tokens/hour (we didn't
%  check it for individual sentences), but that's done only once so it should be amortized.}

@@

One of such alternative formalisms is
Abstract Meaning Representation 
%%% Macro broken?
%(AMR; \inparcite{banarescu2013amr}). 
\parcite{banarescu2013amr}. 
AMR is being actively developed with 
%the view to 
a view towards
using it as a way of generating 
translations but AMR graphs are not aligned to the words in the sentences. Having more abstract semantic structures 
makes the link between source words, target words, and structures more complex and potentially less useful. 
Furthermore, AMR  has been developed mainly with English in mind, and it remains
to be seen how universal AMR graphs are. See
\shortcite{amr:interlingua:lrec:2014} for first observations of divergences
between English 
%vs.
vs.\ 
Chinese and
Czech AMRs.

Another possible semantic framework for this kind of MT evaluation is Semantic
Role Labelling 
%(SRL; \inparcite{palmer2010semantic}).
\parcite{palmer2010semantic}.
SRL has been used in a human translation metric called HMEANT~\parcite{lo2011structured}. 
HMEANT uses semantic role labels
to measure how much of the “who, why, when,
where” has been preserved in translation. Annotators are instructed to identify verbs as
heads of semantic frames. Then they attach role
fillers to the heads and finally they align heads
and role fillers in the candidate translation with
those in a reference translation. Using SRL for evaluating SMT has a number of
disadvantages as explored by
\shortcite{birch-EtAl:2013:WMT} for German, \shortcite{bojar:wu:ssst:2012} for
Czech and by \shortcite{chuchunkov-tarelkin-galinskaya:2014:SSST-8} for Russian.
The most important drawbacks are as follows:
\begin{itemize}
\item SRL frames are based around a verb which is particularly problematic for
copular verbs and  when verbs are translated correctly as nouns or correctly
omitted (the verb ``to be'' in some Russian constructions).
\item SRL frames do not cover the entire source sentence and the semantic structure is
therefore not completely defined, importantly links between frames are not
considered and prepositional phrases which attach to nouns are not marked.
\item Even considering a limited set of eleven roles (agent, patient,
experiencer, locative etc.) is problematic because we cannot assume that these roles will 
 remain stable across different languages. 
 When looking at an automatically parsed  English-Chinese  parallel corpora,
 it was shown that 8.7\% of the arguments do not preserve their semantic
 roles~\parcite{fung2006automatic}. 
\end{itemize}

@@

\bibliography{main}
\bibliographystyle{acl_natbib}
